Parameter Inference\\with Bifurcation Diagrams

### 2021-10-25 docs/appendix.tex
Updates from Overleaf

\begin{figure}[ht]
\centering
\setlength\unitlength{1cm}
{\phantomsubcaption\label{fig:double-exclusive-optima:parameters}}
{\phantomsubcaption\label{fig:double-exclusive-optima:models}}
\includegraphics[width=13cm]{double-exclusive-optima}
\begin{picture}(0,0) \put(-9,6.3){\subref{fig:double-exclusive-optima:parameters}} \end{picture}
\begin{picture}(0,0) \put(-3,6.3){\subref{fig:double-exclusive-optima:models}}
\end{picture}
\caption{Bifurcation inference for the \emph{double exclusive reporter}. \subref{fig:double-exclusive-optima:parameters}. Optimal parameter estimates $\theta^*$ for the targets $\targets=\{4,5\}$ reveal four clusters of qualitatively different regimes: mutual activation ($a_1 < 1$; cluster 1) and mutual inhibition ($a_1 > 1$; cluster 2). \subref{fig:double-exclusive-optima:models}. Example bifurcation diagrams indicate positively and negatively correlated dependencies between the two model states, as a function of the control condition.}
\label{fig:double-exclusive-optima}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\setlength\unitlength{1cm}
{\phantomsubcaption\label{fig:double-exclusive-optima:parameters}}
{\phantomsubcaption\label{fig:double-exclusive-optima:models}}
\includegraphics[width=13cm]{double-exclusive-optima}
\begin{picture}(0,0) \put(-13,7){\subref{fig:double-exclusive-optima:parameters}} \end{picture}
\begin{picture}(0,0) \put(-7,7){\subref{fig:double-exclusive-optima:models}}
\end{picture}
\caption{Bifurcation inference for the \emph{double exclusive reporter}. \subref{fig:double-exclusive-optima:parameters}. Optimal parameter estimates $\theta^*$ for the targets $\targets=\{4,5\}$ reveal four clusters of qualitatively different regimes: mutual activation ($a_1 < 1$; cluster 1) and mutual inhibition ($a_1 > 1$; cluster 2). \subref{fig:double-exclusive-optima:models}. Example bifurcation diagrams indicate positively and negatively correlated dependencies between the two model states, as a function of the control condition.}
\label{fig:double-exclusive-optima}
\end{figure}
